Group 1: Tennis 

### 2019-12-07 Group1Prez.Rmd
Finally Got Table working

---
title: "Group 1: Tennis "
author: "Olivia Beck, Emma Wilson, Ryan Volkert"
date: "December 12, 2019"
output: beamer_presentation
---

```{r setup, include=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = FALSE)
source("funs.R")
library(knitr)
library(kableExtra)
library(tidyverse)
set.seed(400)
```

>>>>

---
title: "Group 1: Tennis "
author: "Olivia Beck, Emma Wilson, Ryan Volkert"
date: "December 12, 2019"
output: beamer_presentation
header-includes: 
  - \usepackage{booktabs} 
  - \usepackage{longtable} 
  - \usepackage{array} 
  - \usepackage{multirow} 
  - \usepackage{wrapfig} 
  - \usepackage{float} 
  - \usepackage{colortbl} 
  - \usepackage{pdflscape} 
  - \usepackage{tabu} 
  - \usepackage{threeparttable} 
  - \usepackage{threeparttablex} 
  - \usepackage[normalem]{ulem} 
  - \usepackage{makecell} 
  - \usepackage{xcolor}

---

```{r setup, include=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = FALSE)
source("funs.R")
library(knitr)
options(kableExtra.latex.load_packages = FALSE) 
library(kableExtra)
library(tidyverse)
set.seed(400)
```
